Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-04-25 ms/sections/discussion2.tex
few last changes to discussion

Phenotypic plasticity could be another cause for dewlap color variation between habitats, where different conditions would favor different phenotypes in different habitats, without genetic changes. Indeed, the yellow, orange and red colors in anoline dewlaps are produced by pterins and carotenoids \citep{Ortiz1962, Ortiz1962a, Ortiz1963, Ortiz1966, Macedonia2000, Steffen2007, Steffen2009}. Animals can be synthesize pterins from nucleotides, but lack the ability to synthesize carotenoids \citep{Goodwin1984, Hill2002, Hill2006}. Different food qualities across sites within islands could therefore potentially cause detectable differences in coloration. Alternatively, more subtle effects on dewlap color could arise from developmental plasticity and depend, e.g. on differences in egg-rearing conditions. However, more data are needed to test these hypotheses, and although some work has shown plastic responses of dewlap color in response to parasites in \textit{A. sagrei} \citep{Cook2013}, we find it unlikely to account for the widespread habitat differences we found. Besides, studies testing the effect of carotenoid deprivation \citep{Steffen2010, Ng2013} and heritability \citep{Cox2017} of dewlap coloration in \textit{A. sagrei} and another species with a carotenoid-based dewlap, \textit{A. distichus}, found little support for phenotypic and developmental plasticity in dewlap coloration.\\

@@

A number of alternative explanations remain. First, there could sexual selection for different dewlap colors in different locations. Indeed, although the sensory-drive hypothesis may include a sexual selection aspect, e.g. if the optimal male phenotype in a given habitat is a function of female perception, sexual preferences may also be arbitrary and independent of the habitat \citep{Andersson1994}, and so could differ across habitats and islands. However, one previous study has found no link between dewlap coloration and body size dimorphism in \textit{A. sagrei} (a proxy for the intensity of sexual selection) in an among-island comparison \citep{Baeckens2018}, and although within-island data are lacking, this scenario may have little plausibility.\\

>>>>

Phenotypic plasticity could be another cause for dewlap color variation between habitats, where different conditions would favor different phenotypes in different habitats, without genetic changes. Indeed, the yellow, orange and red colors in anoline dewlaps are produced by pterins and carotenoids \citep{Ortiz1962, Ortiz1962a, Ortiz1963, Ortiz1966, Macedonia2000, Steffen2007, Steffen2009}. Animals can synthesize pterins from nucleotides, but lack the ability to synthesize carotenoids \citep{Goodwin1984, Hill2002, Hill2006}. Different food qualities across sites within islands could therefore potentially cause detectable differences in coloration. Alternatively, more subtle effects on dewlap color could arise from developmental plasticity and depend, e.g. on differences in egg-rearing conditions. However, more data are needed to test these hypotheses, and although some work has shown plastic responses of dewlap color in response to parasites in \textit{A. sagrei} \citep{Cook2013}, we find it unlikely to account for the widespread habitat differences we found. Besides, studies testing the effect of carotenoid deprivation \citep{Steffen2010, Ng2013} and heritability \citep{Cox2017} of dewlap coloration in \textit{A. sagrei} and another species with a carotenoid-based dewlap, \textit{A. distichus}, found little support for phenotypic and developmental plasticity in dewlap coloration.\\

@@

A number of alternative explanations remain. First, there could sexual selection for different dewlap colors in different locations. Indeed, although the sensory-drive hypothesis may include a sexual selection aspect, e.g. if the optimal male phenotype in a given habitat is a function of female perception, sexual preferences may also be arbitrary and independent of the habitat \citep{Andersson1994}, and so could differ across habitats and islands. Although one previous study has found no link between dewlap coloration and body size dimorphism in \textit{A. sagrei} (a proxy for the intensity of sexual selection) in an among-island comparison \citep{Baeckens2018}, within-island data are lacking to test the plausibility of this scenario.\\
